A Data-Driven Framework for Neural Field Modeling

### 2010-12-29 ltx/first_order_framework/LaTeX_Manuscript.tex
updated the correlation analysis for finding kernel support in first order paper

Now we define the state disturbance as
\begin{equation}\label{eq:Wt} 
	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, d\mathbf{r}},
\end{equation}
which is a zero mean normally distributed white noise process with covariance (see \ref{App:ColoredNoise} for the derivation)
\begin{equation}
	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}. 
\end{equation}
The observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation}
	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
\end{equation}
\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate to reduced model observations from the full model.} The observation equation is linear and can be written in the more compact form
\begin{equation}\label{ObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where each element of the observation matrix is 
\begin{equation}
	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'.
\end{equation}

@@

\subsection{Estimation of Connectivity Kernel Support}
The support of the connectivity kernel can be inferred using spatial correlation analysis. The method presented in this paper is based on a similar published method, where the kernel support was estimated using correlation analysis for a linear system described by an IDE~\citep{Scerri2009}. To demonstrate the method for the neural field model, we first define the spatial cross-correlation function between consecutive observations as 
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}_n\right)\right] \\
	&= \mathbf{E}\left[\left(\int_{\Omega}{
	    m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
	\, d\mathbf{r}'} + 
	\boldsymbol{\varepsilon}_t\right)\left(\int_{\Omega}{
	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_{t+1}\left(\mathbf{r}'\right)
	\, d\mathbf{r}'} + 
	\boldsymbol{\varepsilon}_{t+1}\right)\right] \\
	&= \mathbf{E}\left[\int_{\Omega}{
	    m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
	\, d\mathbf{r}'}\int_{\Omega}{
	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_{t+1}\left(\mathbf{r}'\right)
	\, d\mathbf{r}'} \right]
\end{align}
where $\mathbf{E}[\cdot]$ is the expected value. Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}\right) +T_s \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}+ e_t\left(\mathbf{r}\right)\right)\, d\mathbf{r}'} \right] \\	
	 &= \xi\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)	\, d\mathbf{r}'}\int_{\Omega}
{m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] \nonumber \\
	&+ T_s\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'}\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}\, d\mathbf{r}'} \right] \nonumber \\
	&+ \mathbf{E}\left[ \int_{\Omega} { m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \,d\mathbf{r}' }\int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) e_t \left(\mathbf{r}\right)\, d\mathbf{r}' } \right]
	\label{eq:spatialxcorr}
\end{align}

The first term on the right hand side of equation~\ref{eq:spatialxcorr} is
\begin{equation}
	\xi\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)	\, d\mathbf{r}'}\int_{\Omega}
{m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] = \xi R_{y_{t},y_{t}}(\mathbf{\tau}),
\end{equation}
which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$. DOES THIS GIVE US AN ESTIMATE OF THE FIELD DISTURBANCE COVARIANCE? NUMERICALLY IT SEEMS TO GIVE SOMETHING VERY CLOSE. DEPENDS ON THE BANDWIDTH OF M. The last term on the right hand side of equation~\ref{eq:spatialxcorr} equates to zero since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$. The middle term is
\begin{equation}
	T_s\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'}\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}\, d\mathbf{r}'} \right] = T_s\mathbf{E}\left[y_t(\mathbf{r}_n+\boldsymbol{\tau})\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) g_t(\mathbf{r})\, d\mathbf{r}'} \right],
\end{equation}
where
\begin{equation}
	g_t\left( \mathbf{r} \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left( \mathbf{r}' \right) \right)\, d\mathbf{r}'}. 
\end{equation}
% Therefore we can write
% \begin{equation}
% 	R_{v_{t},v_{t+1}}(\mathbf{\tau}) = \xi R_{v_{t},v_{t}}(\mathbf{\tau}) + T_s R_{v_{t},g_{t}}(\mathbf{\tau})
% \end{equation}
% and
% \begin{equation}\label{eq:xcorr_firing_and_field}
% 	T_s R_{v_{t},g_{t}}(\mathbf{\tau}) = R_{v_{t},v_{t+1}}(\mathbf{\tau})-\xi R_{v_{t},v_{t}}(\mathbf{\tau}).
% \end{equation}
% The spatial cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$ depends on the shape of the spatial mixing kernel $w\left( \mathbf{r},\mathbf{r}' \right)$. Furthermore, the sign (polarity) of $R_{v_{t},g_{t}}(\mathbf{\tau})$ will be the same as the $w\left( \mathbf{r},\mathbf{r}' \right)$ for a given spatial location since the sigmoid function $f\left( v_t\left( \mathbf{r}' \right) \right) > \mathbf{0}$. Therefore, the support of the kernel can be inferred given the cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$. The right hand side of equation~\ref{eq:xcorr_firing_and_field} can be calculated from data if $\xi$ is known. However, since $\xi$ is a decay parameter, we know that $\xi \in (0,1)$. Also, if we assume that
% \begin{equation}
% 	\xi R_{v_{t},v_{t}}(\mathbf{\tau}) \gg T_s R_{v_{t},g_{t}}(\mathbf{\tau})
% \end{equation}
% and
% \begin{equation}
% 	R_{v_{t},g_{t}}(\mathbf{0}) > 0,
% \end{equation}
% which corresponds to local excitation, then we can guess $\xi$ by incrementally increasing it from zero and evaluating equation~\ref{eq:xcorr_firing_and_field} until $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$. The value of $\xi$ before $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$ will provide the approximation.

@@

{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah recording array and the twisted bipolar current source.

>>>>

Now we define the state disturbance as
\begin{equation}\label{eq:Wt} 
	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, d\mathbf{r}},
\end{equation}
which is a zero mean normally distributed white noise process with covariance (see \ref{App:ColoredNoise} for the derivation)
\begin{equation}
	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}. 
\end{equation}
The observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation}
	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
\end{equation}
\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate the reduced model observations from the full model.} The observation equation is linear and can be written in the more compact form
\begin{equation}\label{ObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where each element of the observation matrix is 
\begin{equation}
	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'.
\end{equation}

@@

\subsection{Estimation of Connectivity Kernel Support}
The support of the connectivity kernel can be inferred using spatial correlation analysis. The method presented in this paper is based on a similar published method, where the kernel support was estimated using correlation analysis for a linear system described by an IDE~\citep{Scerri2009}. To demonstrate the method for the neural field model, we first define the spatial cross-correlation function between consecutive observations as 
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}_n\right)\right] \\
	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}_n\right)\right) \right], \label{eq:ObsXCorr}
\end{align}
where $\mathbf{E}[\cdot]$ is the expected value. Since the observation noise is temporally white and independent of the field, equation~\ref{eq:ObsXCorr} reduces to
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
	&=\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right],
\end{align}
where $\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)$ is the noise-free observation.

Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} + e_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'} \right] \\	
	 &= \xi\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) d\mathbf{r}'} \right] \nonumber \\
	&+ T_s\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'} \right] \nonumber \\
	&+ \mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right)\int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) e_t \left(\mathbf{r}'\right)\, d\mathbf{r}' } \right]
	\label{eq:spatialxcorr}
\end{align}

The first term on the right hand side of equation~\ref{eq:spatialxcorr} is
\begin{equation}
	\xi\mathbf{E}\left[\bar{y}_t\left(\mathbf{r}_n + \boldsymbol{\tau}\right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] = \xi R_{\bar{y}_{t},\bar{y}_{t}}(\boldsymbol{\tau}),
\end{equation}
which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$. DOES THIS GIVE US AN ESTIMATE OF THE FIELD DISTURBANCE COVARIANCE? NUMERICALLY IT SEEMS TO GIVE SOMETHING VERY CLOSE. DEPENDS ON THE BANDWIDTH OF M. The last term on the right hand side of equation~\ref{eq:spatialxcorr} equates to zero since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$.

To understand the middle term, the sigmoid activation function, $f(\cdot)$, is approximated by the piecewise function
\begin{equation}
	\hat{f}(v_t(\mathbf{r}')) = \left\{ \begin{array}{ll}
		0, & v_t(\mathbf{r}') \le v_1 \\
		\varsigma v_t(\mathbf{r}'), &  v_1 < v_t(\mathbf{r}') < v_2 \\
		1, & v_t(\mathbf{r}') \ge v_2 \\ 
		\end{array}\right.
\end{equation}

Evaluating the middle term for the case where the field is in the linear region of the nonlinearity gives
\begin{align}
	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \\
	&=T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) \varsigma v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \label{eq:preswap}  \\
	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_\Omega {  m\left(\mathbf{r}'-\mathbf{r}''\right) v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \label{eq:postswap} \\
	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],	
\end{align}
where the associativity and commutativity algebraic properties of the spatial convolution where used to move from equation~\ref{eq:preswap} to equation~\ref{eq:postswap}.

Evaluating the middle term for the saturation regions. If $v_t(\mathbf{r}') \le v_1$ then the middle term will equate to zero. If $v_t(\mathbf{r}') \ge v_2$ then we get
\begin{align}
	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \\
	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'}\right] \\
	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
\end{align}
where $a_1$ is the integral of the connectivity kernel and $a_2$ is the integral of the observation kernel.

Under the assumption that the field is in the linear region of the sigmoid for the majority of time then
\begin{equation}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi R_{  \bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
\end{equation}
The autocorrelation of the noisy observations is
\begin{equation}
	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2
\end{equation}

% Therefore we can write
% \begin{equation}
% 	R_{v_{t},v_{t+1}}(\mathbf{\tau}) = \xi R_{v_{t},v_{t}}(\mathbf{\tau}) + T_s R_{v_{t},g_{t}}(\mathbf{\tau})
% \end{equation}
% and
% \begin{equation}\label{eq:xcorr_firing_and_field}
% 	T_s R_{v_{t},g_{t}}(\mathbf{\tau}) = R_{v_{t},v_{t+1}}(\mathbf{\tau})-\xi R_{v_{t},v_{t}}(\mathbf{\tau}).
% \end{equation}
% The spatial cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$ depends on the shape of the spatial mixing kernel $w\left( \mathbf{r},\mathbf{r}' \right)$. Furthermore, the sign (polarity) of $R_{v_{t},g_{t}}(\mathbf{\tau})$ will be the same as the $w\left( \mathbf{r},\mathbf{r}' \right)$ for a given spatial location since the sigmoid function $f\left( v_t\left( \mathbf{r}' \right) \right) > \mathbf{0}$. Therefore, the support of the kernel can be inferred given the cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$. The right hand side of equation~\ref{eq:xcorr_firing_and_field} can be calculated from data if $\xi$ is known. However, since $\xi$ is a decay parameter, we know that $\xi \in (0,1)$. Also, if we assume that
% \begin{equation}
% 	\xi R_{v_{t},v_{t}}(\mathbf{\tau}) \gg T_s R_{v_{t},g_{t}}(\mathbf{\tau})
% \end{equation}
% and
% \begin{equation}
% 	R_{v_{t},g_{t}}(\mathbf{0}) > 0,
% \end{equation}
% which corresponds to local excitation, then we can guess $\xi$ by incrementally increasing it from zero and evaluating equation~\ref{eq:xcorr_firing_and_field} until $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$. The value of $\xi$ before $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$ will provide the approximation.

@@

{\bf Figure 13. Observation kernel experimental setup}. Photograph through a microscope of the Utah recording yy and the twisted bipolar current source.
